\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-29 paper.tex
Polished Rachid's suggestions

We identify the needed individual and collaborative cognitive
skills: geometric reasoning and situation assessment based on perspective-taking
and affordance analysis; acquisition and representation of knowledge models for
multiple agents (humans and robots, with their specificities) natural multi-modal dialogue;
human-aware task planning; human-robot joint task achievement.  The article
discusses each of these abilities, presents a working implementation, and shows
how they combine in a coherent and original deliberative architecture for
human-robot interaction. Supported by experimental results, we eventually show
how explicit knowledge management, both symbolic and geometric, proves to be
instrumental to richer and more natural human-robot interactions by pushing for
pervasive, human-level semantics within the robot's deliberative system.

@@

The proposed scheme is specially designed for  interaction, and more particularly cooperative task achievement by one robot and one or several humans - called here the robot human partners. It is applicable to domains such as assistant or service robots in domestic and public places as well as to teammate robots in the factory of the future.

@@

We will show in the sequel that:
\begin{itemize}

\item such architecture allows to achieve advanced grounding in a relatively complex environment 
involving one or several humans and a robot

\item  it is able, thanks to the combination of perspective taking and affordances computation 
and with the help of an inference engine, to provide pertinent knowledge for situated dialog

\item  this architecture provides a framework and and a set of mechanisms that allow 
the robot to reason about the mental state of its human partners

\item  the same set of affordances and induced facts together with an explicit reasoning
on humans and robot abilities in a given context,  allow to synthesize relevant human-robot shared plans

\item  it opens the possibility and provides a propitious context for human-aware planning 
at symbolic as well as at geometric level

@@

Another important aspect of such an architecture is that it has been fully implemented and 
demonstrated on several use cases. It is also noteworthy that it proved to be a pertinent 
framework  for new contributions about human-robot joint  action as well as for multi-disciplinary studies.

While several contributions in the literature provide very interesting insights and contributions 
on one aspect or another, we are not aware of a fully implemented architecture that effectively
combines in a coherent way all the issues mentioned above. Besides, this has been done with an effort
to make explicit all the knowledge involved.

We do not claim that this is the sole architecture that can be designed for such problems nor that it
covers all the issues. Our point here is that it is a fully implemented architecture that allowed us to
identify, refine and combine a number of key cognitive abilities that we believe are necessary. Indeed, 
we show here below that it provided us a mean to develop and explore a number of key features for HRI 
in terms of models and algorithms and their articulation in an integrated decisional system for a 
cognitive and interactive robot.

@@

Figure~\ref{fig|archi} gives an overview of our architecture. An active
knowledge base ({\sc Oro}), conveniently thought as a semantic
blackboard, connects most of the modules: the geometric
reasoning module ({\sc Spark}) produces ar relatively high frequency symbolic assertions (like
\stmt{BOOK1 isOn TABLE}) describing the state of the robot environment and its evolution over time. 
These logical statements are stored in the knowledge base, and
queried back, when necessary, by the language processing module ({\sc Dialogs}), the symbolic task
planner (HATP) and the execution controller. The output of the language
processing module and the activities managed by the robot controller are
likewise stored as symbolic statements.

@@

    \node[fill=Purple!50] (thing) {\textbf{thing}};
    \node [below=1.5 of thing] (ptt) {partially tangible thing} edge[dashed] (thing);
        \node [left=of ptt] {physical support} edge (ptt);
        \node [below left=of ptt] {visual mark} edge (ptt);
        \node [below right=of ptt] {container} edge (ptt);
        \node [right=of ptt] {fluid} edge (ptt);
        \node [below=1.5 of ptt] (stt) {solid tangible thing} edge (ptt);
            \node [below=1 of stt] {graspable object} edge (stt);
            \node [below left=of stt] {body part} edge (stt);
            \node [left=of stt] {furniture} edge (stt);
            \node [below right=of stt] (ea) {cited agent} edge (stt);
                \node [below=of ea] {human} edge (ea);
                \node [right=of ea] {robot} edge (ea);

@@

\subsection{Summary of the Contribution}

@@

>>>>

We identify the needed individual and collaborative cognitive
skills: geometric reasoning and situation assessment based on perspective-taking
and affordance analysis; acquisition and representation of knowledge models for
multiple agents (humans and robots, with their specificities); natural multi-modal dialogue;
human-aware task planning; human-robot joint task achievement. The article
discusses each of these abilities, presents a working implementation, and shows
how they combine in a coherent and original deliberative architecture for
human-robot interaction. Supported by experimental results, we eventually show
how explicit knowledge management, both symbolic and geometric, proves to be
instrumental to richer and more natural human-robot interactions by pushing for
pervasive, human-level semantics within the robot's deliberative system.

@@

%The proposed scheme is specially designed for  interaction, and more particularly cooperative task achievement by one robot and one or several humans - called here the robot human partners. It is applicable to domains such as assistant or service robots in domestic and public places as well as to teammate robots in the factory of the future.

@@

We present a model of cognitive integration for service robots that:

    \item achieves advanced grounding in complex real environments involving one or
        several humans and a robot;

    \item supports a distributed computation of symbolic knowledge for
        situated dialogue, thanks to the combination of perspective taking,
        affordances computation and logical inference;

    \item provides generic mechanisms for the robot to reason about the mental state
        of its human partners;

    \item reuses the same set of affordances and inferences, together with
        explicit contextual reasoning on humans and robot abilities, to generate
        human-robot shared plans;

    \item exposes a principled approach to integrate a set of complex cognitive
        components in an explicit, semantics-oriented and loosely-coupled
        fashion.

@@

Importantly, this architecture is fully implemented and we demonstrate it on
several robotic platforms and in several actual interaction scenarios. It proved
to be an effective framework for novel contributions about human-robot joint
action, as well as for multi-disciplinary studies.

@@

Figure~\ref{fig|archi} gives an overview of our architecture. An active
knowledge base ({\sc Oro}), conveniently thought as a semantic
blackboard, connects most of the modules: the geometric
reasoning module ({\sc Spark}) produces at relatively high frequency symbolic assertions (like
\stmt{BOOK1 isOn TABLE}) describing the state of the robot environment and its evolution over time. 
These logical statements are stored in the knowledge base, and
queried back, when necessary, by the language processing module ({\sc Dialogs}), the symbolic task
planner (HATP) and the execution controller. The output of the language
processing module and the activities managed by the robot controller are
likewise stored as symbolic statements.

@@

    \node[fill=Purple!50] (thing) {\textbf{thing}};
    \node [below=1.5 of thing] (ptt) {partially tangible thing} edge[dashed] (thing);
        \node [left=of ptt] {physical support} edge (ptt);
        \node [below left=of ptt] {visual mark} edge (ptt);
        \node [below right=of ptt] {container} edge (ptt);
        \node [right=of ptt] {fluid} edge (ptt);
        \node [below=1.5 of ptt] (stt) {solid tangible thing} edge (ptt);
            \node [below=1 of stt] {graspable object} edge (stt);
            \node [below left=of stt] {body part} edge (stt);
            \node [left=of stt] {furniture} edge (stt);
            \node [below right=of stt] (ea) {embodied agent} edge (stt);
                \node [below=of ea] {human} edge (ea);
                \node [right=of ea] {robot} edge (ea);

@@

@@

While several contributions in the literature provide insights and contributions 
on one aspect or another, we are not aware of a fully implemented architecture that effectively
combines in a coherent manner all the points mentioned above.
We do not claim that this represents the only architecture that can be designed
to address such problems, nor that our approach fully addresses each and every
of these issues. Our point here is that it is a fully implemented architecture that allowed us to
identify, refine and combine a number of key cognitive abilities that we believe are necessary. Indeed, 
we show here below that it provided us a mean to develop and explore a number of key features for HRI 
in terms of models and algorithms and their articulation in an integrated decisional system for a 
cognitive and interactive robot.
